HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-09-12 paper/main.tex

Conversely, HMEANT does not penalize errors (e.g., partial semantic compatability,
or negation flip) in a correctly aligned predicate:

@@

While the translation is mostly understandable, the verb {\"u}berspringen is incorrect here
(should be ``auslassen''). HUME allows marking the main verb as Orange, or even red, while
giving partial score for the translation of ``don't'' and of ``meals''. HMEANT may only
mark the predicate as correct, or mark the entire argument structure as an error.

>>>>

Conversely, HMEANT does not penalize errors (e.g., incorrect tense or negation flip) in a correctly aligned predicate:

@@

While the translation is mostly understandable, the verb {\"u}berspringen is incorrectly inflected. HUME allows marking the main verb as Orange, while
marking the translation of the argument (``Malhzeiten'' or ``meals'') as correct. HMEANT may only mark the predicate as correct, or mark the entire argument structure as an error.
